Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-21 paper-filmat.tex
Pointer to ex/reg completion (in response to review)

A number~$n$ such that~$n \realizes_X x$ is called a \emph{realizer} for~$x$
and can be pictured as a concrete representation of the abstract element~$x$.
The \emph{assembly of natural numbers} is the assembly~$(\NN,{=_\NN})$ and the
\emph{assembly of functions~$\NN \to \NN$} is the
assembly~$(X,{\realizes})$ where~$X$ is the set of computable functions~$\NN
\to \NN$ and~$n \realizes f$ if and only if the~$n$-th Turing machine
computes~$f$.

\begin{defn}The \emph{\effective topos}~$\Eff$ is the ex/reg completion of the
category of assemblies.\end{defn}

>>>>

A number~$n$ such that~$n \realizes_X x$ is called a \emph{realizer} for~$x$
and can be pictured as a concrete representation of the abstract element~$x$.
The \emph{assembly of natural numbers} is the assembly~$(\NN,{=_\NN})$ and the
\emph{assembly of functions~$\NN \to \NN$} is the
assembly~$(X,{\realizes})$ where~$X$ is the set of computable functions~$\NN
\to \NN$ and~$n \realizes f$ if and only if the~$n$-th Turing machine
computes~$f$. The category of assemblies is a regular category, but it is
missing \effective quotients. The \effective topos is obtained by a suitable
completion procedure:

\begin{defn}The \emph{\effective topos}~$\Eff$ is the ex/reg completion (as
in~\cite[Section~3.4]{menni:exact}) of the category of assemblies.\end{defn}
